PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
RE-reviewed sex/gender/age exclusion chunks

```{r coping glad phq summary labels}
summarytools::dfSummary(
  coping.glad.phq.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

```{r select phq little}
coping.glad.phq.raw %>%
  select(contains("little")) %>%
  colnames
```

@@

Maximum is fine with 3 x 7.

@@

Check duplicates again to be save
+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
```{r glad Check duplicates}
dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)

@@

#Exclusion
Exclude those without sex, age and incomplete PHQ/GAD items
Create a new new object for each exclusion step, e.g., data.no_sex and data.no_sex.no_age
```{r Exclude participants that do not report sex}
dim(dat.glad.raw)
dat.no.sex <- dat.glad.raw %>%
  drop_na(Gender)
dim(dat.no.sex)

@@

```{r Exclude participants that do not report age}
dim(dat.no.sex)
dat.no.sex.no.age <- dat.no.sex %>%
  drop_na(age_category)
dim(dat.no.sex.no.age)

dim(dat.no.sex)[1]-dim(dat.no.sex.no.age)[1]
```
`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.age)[1]` were excluded because they did not report their age

>>>>

```{r coping glad phq summary labels}
summarytools::dfSummary(
  coping.glad.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

Will need to double check these namings once we have the new cleaned data -- KT. 

@@

@@

Check duplicates again to be saved
+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
+++KT: No duplicates identified by ID in GLAD. 
```{r glad Check duplicates}
dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)

@@

#Exclusion
Exclude those without sex, gender, age and incomplete PHQ/GAD items
Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
```{r Exclude participants that do not report sex}
dim(dat.glad.raw)
dat.no.sex <- dat.glad.raw %>%
  drop_na(Sex)
dim(dat.no.sex)

@@

```{r Exclude participants that do not report gender}
dim(dat.no.sex)
dat.no.sex.no.gender <- dat.no.sex %>%
  drop_na(Gender)
dim(dat.no.sex.no.gender)

dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
```
`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex

```{r Exclude participants that do not report age}
dim(dat.no.sex.no.gender)
dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
  drop_na(age_category)
dim(dat.no.sex.no.gender.no.age)

dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
```
`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
